Speed and Precision in Range Analysis \\ Technical Report LLP002-2012

### 2012-08-29 doc/Manuscript/CLSC/paper.tex
CLSC: added hyperrefs
Changed paper into a technical report.

% Packages that I must import to compile this latex file:
\usepackage{amssymb}    % To use \mathbb
\usepackage{amsmath}    % To use the equation environment
\usepackage{graphicx}   % For includegraphics
\usepackage{mathpartir} % To use \inferrule

\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

@@

\title{Speed and Precision in Range Analysis}

>>>>

% Packages that I must import to compile this latex file:
\usepackage{amssymb}    % To use \mathbb
\usepackage{amsmath}    % To use the equation environment
\usepackage{graphicx}   % For includegraphics
\usepackage{mathpartir} % To use \inferrule
\usepackage{hyperref}	% FIXME: Don't know if it's necessary

%\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
%T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

@@

\title{Speed and Precision in Range Analysis \\
Technical Report LLP002-2012}
